### 2020-10-09 about/vita.tex
Lots of changes

\font\elevensc=cmcsc11  % For section headers
\font\bigbold=cmb12  % Name
\font\tenb=cmb10
\font\mc=cmr9

@@

@@

\leftright{\bigbold Marcel K.\ Goh}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{URL: marcelgoh.github.io}{+1\thinspace\up(438\up)\thinspace 886-2338}

@@

\leftright{\bf McGill University}{\bf September 2017 -- May 2021}
\leftright{\sl BSc, Honours Mathematics and Computer Science, minor Linguistics}{\sl Montr\'eal, QC, Canada}
CGPA: 3.79/4.
\medbreak
\leftright{\bf Charles University}{\bf February -- June 2019}
\leftright{\sl Exchange semester, Faculty of Mathematics and Physics}{\sl Prague, Czech Republic}
Grade: 1 on all courses (highest score attainable).

@@

\leftright{\bf Sorting algorithms on manifolds}{\bf May 2020 -- present}
\leftright{\sl Summer research project}{\sl McGill University}
\smallskip
Summer research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript.
\medbreak

\leftright{\bf Interactive proofs}{\bf September -- December 2019}
\leftright{\sl Honours research project}{\sl McGill University}
\smallskip
Semester-long research project in the Computation and Logic Group, supervised
by Brigitte Pientka.
Proved a theorem in constructive logic concerning the formal verification
of an interactive proof assistant and wrote OCaml code as part of
ongoing work on the functional programming language Beluga.
\medbreak

@@

@@

\leftright{\bf Department of Mathematics and Statistics, McGill University}{\bf September 2019 -- present}
\leftright{\sl Student Grader}{\sl Montr\'eal, QC, Canada}
\smallskip
Graded MATH 235, an introductory course on the theory of groups, rings, and fields, in Fall 2019
and MATH 240, a discrete mathematics course, in Winter 2020.
\medbreak

@@

@@

@@

{\bf Programming Languages}\par
\CEE, OCaml, Haskell, Standard ML, Scheme Lisp, PostScript, {\tt CWEB}, {\tt MIXAL}, Python
\medbreak

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$0.40 in Knuth reward cheques.

>>>>

% From cwebmac: Date and time
\def\today{\ifcase\month\or
  January\or February\or March\or April\or May\or June\or
  July\or August\or September\or October\or November\or December\fi
  \space\number\day, \number\year}
\newcount\twodigits
\def\hours{\twodigits=\time \divide\twodigits by 60 \printtwodigits
  \multiply\twodigits by-60 \advance\twodigits by\time :\printtwodigits}
\def\gobbleone1{}
\def\printtwodigits{\advance\twodigits100
  \expandafter\gobbleone\number\twodigits
  \advance\twodigits-100 }

\font\eightrm=cmr8
\font\elevensc=cmcsc11  % For section headers
\font\bigbold=cmb12  % Name
\font\tenb=cmb10
\font\mc=cmr9

@@

\def\datethis{\eightrm Last updated \today\ at\ \hours.}

@@

\footline{\phantom{\datethis}\hss\folio\hss\datethis}  % \phantom for centering

\leftright{\bigbold Marcel K.\ Goh}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{URL: marcelgoh.github.io}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\leftright{\bf McGill University}{\bf September 2017 -- April 2021}
\leftright{\sl BSc, Honours Mathematics and Computer Science, minor Linguistics}{\sl Montr\'eal, QC, Canada}
CGPA: 3.79/4.
\medbreak
\leftright{\bf Charles University}{\bf February -- June 2019}
\leftright{\sl Exchange semester, Faculty of Mathematics and Physics}{\sl Prague, Czech Republic}
Grade: 1 on all courses (highest score attainable).

@@

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal weekly seminars over the summer, discussing
various topics related to branching
processes. (Gave a presentation at three of these: one on root estimation in Galton-Watson
trees, and two on generating functions and elementary analytic combinatorics.)

\medbreak
\leftright{\bf Sorting algorithms on manifolds}{\bf May -- August 2020}
\leftright{\sl Summer research project}{\sl McGill University}
\smallskip
Research project under the supervision of Michael Lipnowski.
Studied algorithms that investigate the topology of group actions on locally symmetric spaces.
Work involved writing of code in OCaml and PostScript that generates illustrations of certain quotient
spaces, in various models of hyperbolic geometry.
\medbreak

\leftright{\bf Interactive proofs}{\bf September -- December 2019}
\leftright{\sl Honours research project}{\sl McGill University}
\smallskip
Semester-long research project in the Computation and Logic Group, supervised
by Brigitte Pientka.
Proved a theorem in constructive logic concerning the formal verification
of the interactive proof assistant Harpoon and wrote OCaml code as part of
ongoing work on the functional programming language Beluga.
\medbreak

@@

\filbreak

@@

\leftright{\bf Department of Mathematics and Statistics, McGill University}{\bf September 2019 -- present}
\leftright{\sl Student Grader}{\sl Montr\'eal, QC, Canada}
\smallskip
Grading of assignments in the following courses:
\begingroup\parindent=10pt
\smallskip
\thing Fall 2020: MATH 323 Probability, MATH 456 Honours Algebra 3
\smallskip
\thing Winter 2020: MATH 240 Discrete Structures
\smallskip
\thing Fall 2019: MATH 235 Algebra 1
\endgroup
\medbreak

@@

\leftright{\bf Bakir Contracting Corp.}{\bf May -- August 2018}
\leftright{\sl Painter}{\sl Edmonton, AB, Canada}
\smallskip
Exterior painting (siding, decks, fences, trim, etc.) for residential clients.
\medbreak

@@

\leftright{\bf YoWoChAs Outdoor Education Centre}{\bf June -- August 2014}
\leftright{\sl Summer Camp Counsellor}{\sl Fallis, AB, Canada}
\smallskip
Led children aged 4--15 through various activities (e.g. archery, canoeing, zipline) at a sleepaway camp.
\medbreak

@@

{\bf Programming Languages}\par
\CEE, OCaml, Haskell, Standard ML, Scheme Lisp, PostScript, {\tt CWEB}, {\tt MIXAL}, Python.
\medbreak

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$0.40 in Knuth reward cheques.
\medbreak

\filbreak
